The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-05-04 paper/paper.tex
Update paper.tex
Minor typo
typo

After this seection, and cuts to contiguous geographic regions, we used around 20M objects from the Buzzard
simulations and around 36M objects the CosmoDC2 simulations.

@@

\begin{table*}[]
	\begin{tabular}{|l|p{8cm}|c|}
	\hline
	\textbf{Name} & \textbf{Description} & \textbf{Submitters} \\
	\hline
	\textsc{Random} & Random assignment (control method)  & Organizers \\
	\textsc{IBandOnly} & i-band only (control method)  & Organizers \\
	\textsc{RandomForest} & A collection of individual decision trees & Organizers \\
	\textsc{LSTM} & Long Short-Term Memory neural network & CRB, BF, GT, ESC, EJG \\
	\textsc{AutokerasLSTM}\tablenotemark{a} & Automaticaly configured LSTM variant. & CRB, BF, GT, ESC, EJG \\
	\textsc{LGBM} & Light Gradient Boosted Machine & CRB, BF, GT, ESC, EJG \\
	\textsc{TCN} & Temporal Convolution Network & CRB, BF, GT, ESC, EJG \\
	\textsc{CNN} & Convolutional Neural Network & CRB, BF, GT, ESC, EJG \\
	\textsc{Ensemble} & Combination of three other network methods & CRB, BF, GT, ESC, EJG \\
	\textsc{SimpleSOM} & Self-Organizing Map & AHW \\
	\textsc{PQNLD} & Extension of {\sc SimpleSom} combining with template-based redshift estimation & AHW \\
	\textsc{UTOPIA} & Nearest-neighbours, optimised in the limit of large representative training sets & AHW \\
	\textsc{ComplexSOM} & Extension of {\sc SimpleSom} with an additional assignment optimization & DA, AHW, AN, EG, AB \\
	\textsc{GPzBinning} & Gaussian Process redshift estimator and binner & PH \\
	\textsc{JaxCNN/JaxResnet} & Two related CNN-based bin edge optimizers & AP \\
	\textsc{NeuralNetwork1/2} & Dense network optimizing bin assignment for two metrics & AP \\
	\textsc{PCACluster} & Principal Component Analysis of fluxes then optimized clustering & DG \\
	\textsc{ZotBin/ZotNet} & Two related neural network methods with a preprocesing normalizing flow & DK \\
	\textsc{FFNN} & Deed-forward neural network & EN \\
	\textsc{FunBins} & Random forest with various nominal bin edge selection & AB \\
	\textsc{MLPQNA} & Multi-layer perceptron & SC, MB \\
	\textsc{Stacked Generalization} & Combination of gradient tree boosting and logistic regression & JEC\\
	\hline
	\end{tabular}
	\caption{Methods entered into the challenge. The algorithms are described more fully in \autoref{app:methods}.}
	\label{tab:entrants}
	\tablenotetext{a}{A technical problem, involving conflicting versions of libraries and incompatible hardware, meant that AutoKerasLSTM could not be run in the final challenge.}
\end{table*}

>>>>

After this section, and cuts to contiguous geographic regions, we used around 20M objects from the Buzzard
simulations and around 36M objects the CosmoDC2 simulations.

@@

\begin{table*}[]
	\begin{tabular}{|l|p{8cm}|c|}
	\hline
	\textbf{Name} & \textbf{Description} & \textbf{Submitters} \\
	\hline
	\textsc{Random} & Random assignment (control method)  & Organizers \\
	\textsc{IBandOnly} & i-band only (control method)  & Organizers \\
	\textsc{RandomForest} & A collection of individual decision trees & Organizers \\
	\textsc{LSTM} & Long Short-Term Memory neural network & CRB, BF, GT, ESC, EJG \\
	\textsc{AutokerasLSTM}\tablenotemark{a} & Automaticaly configured LSTM variant. & CRB, BF, GT, ESC, EJG \\
	\textsc{LGBM} & Light Gradient Boosted Machine & CRB, BF, GT, ESC, EJG \\
	\textsc{TCN} & Temporal Convolution Network & CRB, BF, GT, ESC, EJG \\
	\textsc{CNN} & Convolutional Neural Network & CRB, BF, GT, ESC, EJG \\
	\textsc{Ensemble} & Combination of three other network methods & CRB, BF, GT, ESC, EJG \\
	\textsc{SimpleSOM} & Self-Organizing Map & AHW \\
	\textsc{PQNLD} & Extension of {\sc SimpleSom} combining with template-based redshift estimation & AHW \\
	\textsc{UTOPIA} & Nearest-neighbours, optimised in the limit of large representative training sets & AHW \\
	\textsc{ComplexSOM} & Extension of {\sc SimpleSom} with an additional assignment optimization & DA, AHW, AN, EG, AB \\
	\textsc{GPzBinning} & Gaussian Process redshift estimator and binner & PH \\
	\textsc{JaxCNN/JaxResnet} & Two related CNN-based bin edge optimizers & AP \\
	\textsc{NeuralNetwork1/2} & Dense network optimizing bin assignment for two metrics & FL \\
	\textsc{PCACluster} & Principal Component Analysis of fluxes then optimized clustering & DG \\
	\textsc{ZotBin/ZotNet} & Two related neural network methods with a preprocesing normalizing flow & DK \\
	\textsc{FFNN} & Deed-forward neural network & EN \\
	\textsc{FunBins} & Random forest with various nominal bin edge selection & AB \\
	\textsc{MLPQNA} & Multi-layer perceptron & SC, MB \\
	\textsc{Stacked Generalization} & Combination of gradient tree boosting and logistic regression & JEC\\
	\hline
	\end{tabular}
	\caption{Methods entered into the challenge. The algorithms are described more fully in \autoref{app:methods}.}
	\label{tab:entrants}
	\tablenotetext{a}{A technical problem, involving conflicting versions of libraries and incompatible hardware, meant that AutoKerasLSTM could not be run in the final challenge.}
\end{table*}
